MLH1 data report 

### 2017-11-02 rmd_report.rmd
cleaned up setup file.

```{r, echo=FALSE, include = FALSE}
##FIX ORDER HERE (this should be put in the data setup script)
MLH1_data$strain<- factor(MLH1_data$strain,levels =c("G", "LEWES",
                              "WSB", "PWD","MSM","CAST"), order=T )
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(file.name = factor(file.name)) #another category that you want the order to match
# sort your dataframe, by the focal categories
MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

#Add fake CAST female data
last_row <-data.frame(file.name=c("12dec18_20dec20_CAST_f1_sp1_12_1_rev.tif", "12dec18_20dec20_CAST_f1_sp1_12_2_rev.tif"), Random.Name = c("1234567.tif","123456789.tif"), quality=c(1,1),nMLH1.foci =c(25,22), XY.paired =c("no","no"), REDO.crop =c("no","no"),n =c(20,20), achiasmate=c(0,0),asynased=c(0,0),notes=c("",""),category = c("CAST female","CAST female"), strain= c("CAST","CAST"), sex=c("female","female"),adj_nMLH1.foci=c(25,22),mouse=c("20dec20_CAST_f1","20dec20_CAST_f1") )

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci)) + geom_boxplot(data = MLH1_data, aes(fill = factor(strain) ) ) + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen"))
ff <- ff + facet_wrap(~ sex, scales="free")
ff
```

@@

qq <- ggplot(highest_qual_df, aes(x = mouse, y = adj_nMLH1.foci)) + geom_boxplot(data = highest_qual_df, aes(fill = factor(strain) ) ) +  ggtitle("Cells with quality scores of 2 or 1") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",
  "coral1", "#E69F00", "yellowgreen"))
high_qual_boxplot <- qq + facet_wrap(~ sex, scales="free") #this is breaking the kniting... 
```

@@

for(i in 1:(length(df_list))){
 # print(i)
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
 # print(sub_mouse_means)
  #below should work -- I think I need to go througheach row of the df_list[[i]]
  for(o in 1:length(df_list[[i]]$file.name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}
#remove CAST, this column isn't added to MLH1 col, it's added to df_list
#The above adds a column of mouse specific averages to a giant list of dataframes. Each dataframe in the list is specific to a category.
#the next step is to make plots from this giant list of dataframes
# I can delete all of the code below that by hand makes

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
#geom_hline(aes(yintercept = med, group = gr), colour = 'red')
for (gg in 1:length(plot_list) ){
  show(plot_list[gg])
  #invisible(lapply(obj,function(x) plot(x,main="some plot")))
}
```

@@

Currently this section is under construction.
```{r}
colnms = c("mouse", "rep")
ply_data <- df.pasd.mice[df.pasd.mice$mouse == "8oct14_PWD_f8",]
#make this the function that I apply over the mice in the data

#simplify the t.test
t.test(sample(ply_data$nMLH1.foci, 5), sample(ply_data$nMLH1.foci, 5))$p.value
t.test(sample(ply_data$nMLH1.foci, 13), sample(ply_data$nMLH1.foci, 13))$p.value

#repeat the sampling 100 times
bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2

#try with do
blah <- df.pasd.mice %>% group_by(mouse) %>% do(head(.))

plist=data.frame(pv=as.numeric(), mean1=as.numeric(), mean2=as.numeric())

hundred <- function(x){
  plist=data.frame(pv=as.numeric(), mean1=as.numeric(), mean2=as.numeric())
  for(eye in 1:100){
    samp1 = sample(x, 5)
    samp2 = sample(x, 5)
    plist$pv[eye] <- t.test(samp1,samp2)$p.value
    plist$mean1[eye] <- mean(samp1)
    plist$mean2[eye] <- mean(samp2)
  }
  return(plist)
} 
mm <- hundred(ply_data$nMLH1.foci)

#makes dfs, with the samples. // sampling from MLH1
permut.mouse.numb <- function(x, rep_size, samp_size){
  new.df = matrix(nrow=rep_size, ncol=samp_size)
for(i in 1:rep_size) {
  new.df[i,] = sample(x, samp_size)
  }
return(as.data.frame(new.df, colnames(colnms) ) )
  #return sampled
}
#can I integrate the sampling and t.test here?

#function for

#this works. sampling x permutations, y sample size
vv <- permut.mouse.numb(df.pasd.mice$nMLH1.foci,5,4)

## I think this does it! this makes a list of 23 dfs (for each mouse in the large df)
##this makes dfs for doing the t.tests
kk<-dlply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,5) )
#applies permut function over mouse -- then run a t.test and return pvalue
jj<-ddply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,20) )

#
pval <- function()

#t.test and p values
#maybe I should just choose 2 samples, do a t.test, do that 100 times..?
#below runs t.tests on
#this is making a new tab;e, 
bb <- ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )#t.test for 2 samples of size 20

# figure out a way to mush dd into a matrix

repeats = 10
new.p.matrix = matrix(ncol=length(unique(jj$mouse)), nrow = repeats)
for(e in 1:repeats){
  new.p.matrix[e]<- ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )

  }

powrange <- seq(0.4, .9, .1)
n <- sapply(powrange, function(i) power.prop.test(p1=0.4,p2=0.24,power=i,sig.level=0.05)$n)
plot(powrange, n)

bb$mouse[(bb$V1 < 0.05)]
#mice which had significantly difference in samples of size 20
#16jan16_G_f2  20feb16_G_f3  3nov15_WSB_f1
#17mar16_G_f1
#16jan16_G_f2   20dec16_LEW_m3
#30sep16_MSM_f2
#22jun15_G_m2

#figure out how to permute these tests. repeat the above... then return distributions of p values

#10
#20feb16_G_f3   13nov16_MSM_m1

#figure out a way to plot/visualize these pvalues
#2 samples are good for t.tests, but I need to repeat 100 times
#I think I need to ... add the replicates that can be xxply through

## for 1:100, cal permt(10,2) then call 
ll=c()
ty <- for(i in 1:10){
  print(i)
  jj <-ddply(df.pasd.mice, .(mouse), function(x) permut.mouse.numb(x$nMLH1.foci,2,10) )

  bb <-ddply(jj, .(mouse), function(x) t.test(x[1,2:5],x[2,2:5])$p.value )
  #the t.test$p.values are not exactly what they should be
#put p values into a list? (100 pvalues )
  ll[i] = bb$V1[i]#this returns a list of p values for different mice? one mouse?
}

#for

gg<-t.test(kk$`10mar15_PWD_m2`[1,2:5], kk$`10mar15_PWD_m2`$V3)  
#jj$`10mar15_PWD_m2`
#jj[1,1:5]
#$`10mar15_PWD_m2`
#[1] 0.6071011

##then do t.test to test the distributions 
## data is the data frames, by mouse, function is t.test

# use q_cut_off table, to find the mice to use
listOmice <- q_cutoff_table$mouse[ (q_cutoff_table$total >= 25) ]
#mke new df with from 
df.pasd.mice <- MLH1_data[MLH1_data$mouse %in% listOmice, ]

#write function --- for taking 100 samples of 10
permut.df <- function(df){
  #semperate by mouse
    mouse.data    <- ddply(df, c("mouse"), summarise,
       df <- data.frame(
              samp = sample(nMLH1.foci,5)
            ) 
        )

  return(mouse.data)
}

mouse.data <- ddply(df.pasd.mice, c("mouse"), summarise,

  m.df <- data.frame(sample(nMLH1.foci, 5, replace = FALSE) )
  )

# this creates dataframe, which is a subset of larger dataframe ... not sure se_alone, but samples 40 of 
this =ddply (df.pasd.mice, .(mouse), subset, sample(seq_along(nMLH1.foci)<=5))
#ss <- sample(df.pasd.mice$nMLH1.foci)

Table_BD_mouse <- ddply(BDMLH1_data, c("ANIMAL_ID", "Cross"), summarise,
                       N  = length(nMLH1_foci),
                       mean_co = format(round( mean(nMLH1_foci), 3), nsmall = 3),
                       var = format(round( var(nMLH1_foci),3), nsmall = 3),
                       sd   = round(sd(nMLH1_foci),3),
                       se   = round(sd / sqrt(N),3)
                       #text=paste(Cross, collapse=""))
)

>>>>

```{r}
#order the data frame
MLH1_data <- with(MLH1_data, MLH1_data[order(sex, strain),])
#set the order of another column, based on another variable (so that when)

MLH1_data <- MLH1_data %>%
  arrange(strain, sex, mouse) %>%
  mutate(Original.Name = factor(Original.Name)) #another category that you want the order to match
# sort your dataframe, by the focal categories
MLH1_data$mouse <- factor(MLH1_data$mouse, levels=unique(MLH1_data$mouse))

#Add fake CAST female data
last_row <-data.frame(Batch = c("100", "100"), X= c("",""), Original.Name=c("12dec18_20dec20_CAST_f1_sp1_12_1_rev.tif", "12dec18_20dec20_CAST_f1_sp1_12_2_rev.tif"), Random.Name = c("1234567.tif","123456789.tif"), quality=c(1,1),nMLH1.foci =c(25,22), XY.paired =c("no","no"), REDO.crop =c("no","no"),n =c(20,20), achiasmate=c(0,0),asynased=c(0,0),notes=c("",""),category = c("CAST female","CAST female"), strain= c("CAST","CAST"), sex=c("female","female"),adj_nMLH1.foci=c(25,22),mouse=c("20dec20_CAST_f1","20dec20_CAST_f1") )

@@

```{r first boxplots, echo=FALSE, fig.align='center'}
ff <- ggplot(MLH1_data, aes(x = as.factor(mouse), y = adj_nMLH1.foci)) + geom_boxplot(data = MLH1_data, aes(fill = factor(strain) ) ) + ggtitle("Boxplots of MLH1 distributions by mouse") + theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",  "coral1", "#E69F00", "yellowgreen", "black", "grey", "lightgrey"))
ff <- ff + facet_wrap(~ sex, scales="free")
ff
```

@@

qq <- ggplot(highest_qual_df, aes(x = mouse, y = adj_nMLH1.foci)) + geom_boxplot(data = highest_qual_df, aes(fill = factor(strain) ) ) +  ggtitle("Cells with quality scores of 2 or 1") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) + scale_fill_manual(values=c("#56B4E9", "cadetblue", "lightblue",
  "coral1", "#E69F00", "yellowgreen","black", "grey"  ))
high_qual_boxplot <- qq + facet_wrap(~ sex, scales="free") #this is breaking the kniting... 
```

@@

for(i in 1:(length(df_list))){
 # print(i)
  df_list[[i]] <- df_list[[i]][!(is.na(df_list[[i]]$quality) | df_list[[i]]$quality==""), ]
  sub_mouse_means <- ddply(df_list[[i]], .(mouse), summarise,
                       mouse_nMLH1 = mean(adj_nMLH1.foci)
  )
 # print(sub_mouse_means)
  #below should work -- I think I need to go througheach row of the df_list[[i]]
  for(o in 1:length(df_list[[i]]$Original.Name)){
    df_list[[i]]$mouse_mean_MLH1[o] <- sub_mouse_means$mouse_nMLH1[ (df_list[[i]]$mouse[o] == sub_mouse_means$mouse) ]
        }
}
#remove CAST, this column isn't added to MLH1 col, it's added to df_list
#The above adds a column of mouse specific averages to a giant list of dataframes. Each dataframe in the list is specific to a category.
#the next step is to make plots from this giant list of dataframes
# I can delete all of the code below that by hand makes

@@

```{r, echo=FALSE, message=FALSE,results='hide', warning=FALSE }
#geom_hline(aes(yintercept = med, group = gr), colour = 'red')
#for (gg in 1:length(plot_list) ){
#  show(plot_list[gg])
  #invisible(lapply(obj,function(x) plot(x,main="some plot")))
#}
```

@@

Currently this section is under construction.
